---
output:
  pdf_document: default
  html_document: default
---
Two related real-world candidate datasets appropriate for the selected theme are clearly described (one main, one back-up)
Show the structure or head of the dataframe.


## GAME PLAn 

nce you download the files, follow these steps:

Open subject_metadata.csv to find the SubjectId that corresponds to "Algebra."

Open question_metadata.csv to find all QuestionIds that are linked to those Algebra IDs.

Filter train_data.csv for those QuestionIds to get the student response records (User ID, Correctness, and Time).

View the corresponding image in the images/ folder to see the actual math problem

```{r, echo=FALSE}}
# Load one candidate dataset
train_data <- read.csv("data/train_data/train_task_1_2.csv")

# Show the first 6 rows
head(train_data)
```

```{r}
# Load the other key datasets (task 1/2)
subject_metadata <- read.csv("data/metadata/subject_metadata.csv")
question_metadata <- read.csv("data/metadata/question_metadata_task_1_2.csv")
student_metadata <- read.csv("data/metadata/student_metadata_task_1_2.csv")
answer_metadata <- read.csv("data/metadata/answer_metadata_task_1_2.csv")

# Show the first 6 rows of each
head(subject_metadata)
head(question_metadata)
head(student_metadata)
head(answer_metadata)
```

```{r}
# Example: build a small joined subset with
# - problem ID
# - student ID
# - whether correct
# - estimated time taken (seconds)
#
# Note: There is no explicit "time taken" column in train_task_1_2.csv.
# Here we estimate it as the time difference between consecutive answers
# by the same student using DateAnswered.

# Keep a small subset for demonstration
subset_train <- train_data[1:3000, c("QuestionId", "UserId", "AnswerId", "IsCorrect")]
subset_answer <- answer_metadata[, c("AnswerId", "DateAnswered")]

# Join on AnswerId
joined_subset <- merge(subset_train, subset_answer, by = "AnswerId", all.x = TRUE)

# Parse answer timestamp
joined_subset$DateAnswered <- as.POSIXct(
	joined_subset$DateAnswered,
	format = "%Y-%m-%d %H:%M:%OS",
	tz = "UTC"
)

# Sort by student and answer time
joined_subset <- joined_subset[order(joined_subset$UserId, joined_subset$DateAnswered), ]

# Estimate time taken per response (within each student)
joined_subset$time_taken_seconds <- ave(
	as.numeric(joined_subset$DateAnswered),
	joined_subset$UserId,
	FUN = function(x) c(NA, diff(x))
)

# Final structure requested
final_example <- joined_subset[, c("QuestionId", "UserId", "IsCorrect", "time_taken_seconds")]
names(final_example) <- c("problem_id", "student_id", "is_correct", "time_taken_seconds")

head(final_example, 10)
```